---
title: "Mo'orea & Tahiti 16s community composition"
author: "Nicola G. Kriefall"
date: "10/7/2021"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
---

# Setup

```{r packages composition}
library(rlang)
library(stringr)
library(dplyr)
library(stats)
library(ggpubr)
library(vegan)
library(cowplot)
library(tidyverse)
#library(MCMC.OTU)
#install.packages("remotes")
#remotes::install_github("Jtrachsel/funfuns")
library("funfuns")
```

Read in data

```{r read in data}
#setwd('/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/mr16s_revised/analysis/03.community_comp')
setwd("/Volumes/GoogleDrive-104519233854090018057/My Drive/Moorea_revisions/moorea_holobiont_revised/mr16s_revised/03.community_comp")

samdf <- read.csv("mr16s_sampledata_plusneg copy.csv",header=TRUE)
load("taxa2 copy.Rdata")

#load("ps.clean.Rdata")
#load("ps.rare.Rdata")
load("ps.rare.trim.Rdata")
load("ps.trim.Rdata")
```

Rename ASVs to be more informative

```{r rename ASVs}
tax <- as.data.frame(ps.rare.trim@tax_table@.Data)

tax.clean <- data.frame(row.names = row.names(tax),
                        Kingdom = str_replace(tax[,1], "D_0__",""),
                        Phylum = str_replace(tax[,2], "D_1__",""),
                        Class = str_replace(tax[,3], "D_2__",""),
                        Order = str_replace(tax[,4], "D_3__",""),
                        Family = str_replace(tax[,5], "D_4__",""),
                        Genus = str_replace(tax[,6], "D_5__",""),
                        Species = str_replace(tax[,7], "D_6__",""),
                        stringsAsFactors = FALSE)
tax.clean[is.na(tax.clean)] <- ""

for (i in 1:7){ tax.clean[,i] <- as.character(tax.clean[,i])}
####### Fill holes in the tax table
tax.clean[is.na(tax.clean)] <- ""
for (i in 1:nrow(tax.clean)){
  if (tax.clean[i,2] == ""){
    kingdom <- paste("Kingdom_", tax.clean[i,1], sep = "")
    tax.clean[i, 2:7] <- kingdom
  } else if (tax.clean[i,3] == ""){
    phylum <- paste("Phylum_", tax.clean[i,2], sep = "")
    tax.clean[i, 3:7] <- phylum
  } else if (tax.clean[i,4] == ""){
    class <- paste("Class_", tax.clean[i,3], sep = "")
    tax.clean[i, 4:7] <- class
  } else if (tax.clean[i,5] == ""){
    order <- paste("Order_", tax.clean[i,4], sep = "")
    tax.clean[i, 5:7] <- order
  } else if (tax.clean[i,6] == ""){
    family <- paste("Family_", tax.clean[i,5], sep = "")
    tax.clean[i, 6:7] <- family
  } else if (tax.clean[i,7] == ""){
    tax.clean$Species[i] <- paste("Genus",tax.clean$Genus[i], sep = "_")
  }
}

tax_table(ps.rare.trim) <- as.matrix(tax.clean)
```

# Core vs. accessory

## Core

```{r packages core, echo=FALSE}
#BiocManager::install("microbiome")
#remotes::install_github("r-lib/rlang")
library(microbiome)
```

```{r core}
pseq.core <- core(ps.trim, detection = 0, prevalence = .7)
pseq.core <- core(ps.rare.trim, detection = 0, prevalence = .7)
pseq.core #9 taxa

#saving
#core.tax <- data.frame(pseq.core@tax_table)
#write.csv(core.tax,"core.taxa.csv")

ps_glom <- tax_glom(pseq.core, "Genus")
ps0 <- transform_sample_counts(ps_glom, function(x) x / sum(x))
ps1 <- merge_samples(ps0, "site_zone")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))

plot_bar(ps2, fill="Genus")+
  geom_bar(stat="identity")+
  theme_cowplot()+
  scale_fill_brewer(palette="BrBG")
#ggsave(file="core.bar.pdf",width=8)

#not rel abun
plot_ordination(pseq.core,ordinate(pseq.core,"PCoA", "bray"),color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")

#rel abun
pseq.core.rel <- transform_sample_counts(pseq.core, function(x) x / sum(x))
plot_ordination(pseq.core.rel,ordinate(pseq.core.rel,"PCoA", "bray"),color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")

#by site
ps.core.mnw <- subset_samples(pseq.core,site=="MNW")
ps.core.mse <- subset_samples(pseq.core,site=="MSE")
ps.core.tnw <- subset_samples(pseq.core,site=="TNW")

plot_ordination(ps.core.mnw,ordinate(ps.core.mnw,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()#+
  #scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  #scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
```

```{r calculate core abundance}
# calculating core abundances #
core.sqs <- tax_table(pseq.core)
core.sqs.ids <- row.names(core.sqs)
core.sqs.ids

ps.rare.trim.rel <- transform_sample_counts(ps.rare.trim, function(x) x / sum(x))
seq.rare.rel <- data.frame(otu_table(ps.rare.trim.rel))
tax.core <- tax_table(ps.rare.trim.rel)

seq.core <- seq.rare.rel %>% select(c(core.sqs.ids))
core.rel <- data.frame(colMeans(seq.core))

total.rel <- data.frame(colMeans(seq.rare.rel))
total.rel.ordered <- data.frame(total.rel[order(-total.rel$colMeans.seq.rare.rel.),,drop=FALSE])
```

### Core stats

```{r core stats}
seq.core <- data.frame(otu_table(pseq.core))
seq.core <- data.frame(otu_table(pseq.core.rel))

dist.core <- vegdist(seq.core)
samdf.core <- data.frame(sample_data(pseq.core))
row.names(samdf.core)==row.names(seq.core)

bet.all <- betadisper(dist.core,samdf.core$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.core,samdf.core$site)
#anova(bet.all)
permutest(bet.all, pairwise = TRUE, permutations = 999) #MSE & TNW different again
# Pairwise comparisons:
# (Observed p-value below diagonal, permuted p-value above diagonal)
#          MNW      MSE   TNW
# MNW          0.186000 0.383
# MSE 0.191245          0.029
# TNW 0.407966 0.036931      
plot(bet.all) 

adonis(seq.core ~ site, data=samdf.core, permutations=999)
adonis(seq.core ~ site/zone, data=samdf.core, permutations=999)
adonis(seq.core ~ zone, strata=samdf.core$site,data=samdf.core, permutations=999)

pairwise.adonis(seq.core, factors = samdf.core$site, permutations = 999)
#MNW only marginally different than TNW surprisingly
#RELATIVE ABUNDANCE:
#        pairs  F.Model         R2 p.value p.adjusted
# 1 MNW vs MSE 3.573894 0.05804236   0.027      0.027 * 
# 2 MNW vs TNW 2.252231 0.03617912   0.096      0.096 .
# 3 MSE vs TNW 7.975852 0.11733361   0.004      0.004 **

#RAREFIED:
#MNW only marginally different than TNW surprisingly
#RELATIVE ABUNDANCE:
#        pairs  F.Model         R2 p.value p.adjusted
# 1 MNW vs MSE 3.404324 0.05828891   0.021      0.021 *
# 2 MNW vs TNW 2.306130 0.04169754   0.090      0.090 . 
# 3 MSE vs TNW 7.078557 0.11589267   0.004      0.004 **
```

### Core stats by zone

```{r core stats zone}
#### MNW ####
# ps.core.mnw <- subset_samples(pseq.core,site=="MNW")
# ps.core.mse <- subset_samples(pseq.core,site=="MSE")
# ps.core.tnw <- subset_samples(pseq.core,site=="TNW")

ps.core.mnw <- subset_samples(pseq.core.rel,site=="MNW")
ps.core.mse <- subset_samples(pseq.core.rel,site=="MSE")
ps.core.tnw <- subset_samples(pseq.core.rel,site=="TNW")

seq.core.mnw <- data.frame(otu_table(ps.core.mnw))

dist.core.mnw <- vegdist(seq.core.mnw)
samdf.core.mnw <- data.frame(sample_data(ps.core.mnw))
row.names(samdf.core.mnw)==row.names(seq.core.mnw)

bet.all <- betadisper(dist.core.mnw,samdf.core.mnw$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.core.mnw ~ zone,data=samdf.core.mnw, permutations=999)
#not sig
#same with rare or rel

#### MSE ####
seq.core.mse <- data.frame(otu_table(ps.core.mse))

dist.core.mse <- vegdist(seq.core.mse)
samdf.core.mse <- data.frame(sample_data(ps.core.mse))
row.names(samdf.core.mse)==row.names(seq.core.mse)

bet.all <- betadisper(dist.core.mse,samdf.core.mse$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.core.mse ~ zone,data=samdf.core.mse, permutations=999)
#           Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)  
# zone       1    0.6122 0.61216  3.9768 0.12838  0.014 *
# Residuals 27    4.1561 0.15393         0.87162         
# Total     28    4.7683                 1.00000         

#### TNW ####
seq.core.tnw <- data.frame(otu_table(ps.core.tnw))

dist.core.tnw <- vegdist(seq.core.tnw)
samdf.core.tnw <- data.frame(sample_data(ps.core.tnw))
row.names(samdf.core.tnw)==row.names(seq.core.tnw)

bet.all <- betadisper(dist.core.tnw,samdf.core.tnw$zone)
anova(bet.all)
plot(bet.all) 
# Analysis of Variance Table
# 
# Response: Distances
#           Df Sum Sq Mean Sq F value  Pr(>F)  
# Groups     1 0.1582 0.15821  5.9475 0.02218 *
# Residuals 25 0.6650 0.02660                  

adonis(seq.core.tnw ~ zone,data=samdf.core.tnw, permutations=999)
#           Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)    
# zone       1   0.89731 0.89731   11.12 0.30787  0.001 ***
# Residuals 25   2.01724 0.08069         0.69213           
# Total     26   2.91455                 1.00000           
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
```

## Accessory

```{r accessory}
ps.rare.trim.otu <- data.frame(ps.trim@otu_table)
#ps.rare.trim.otu <- data.frame(ps.rare.trim@otu_table)
core.tax <- data.frame(pseq.core@tax_table)
core.ids <- c(rownames(core.tax))
ps.rare.trim.acc.otu <- ps.rare.trim.otu[,!colnames(ps.rare.trim.otu) %in% core.ids ]
row.names(samdf) <- samdf$id

#remake phyloseq object
ps.acc <- phyloseq(otu_table(ps.rare.trim.acc.otu, taxa_are_rows=FALSE), 
                         sample_data(samdf), 
                         tax_table(taxa2))
ps.acc #214 taxa accessory

plot_ordination(ps.acc,ordinate(ps.acc,"PCoA", "bray"),color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
#ggsave(file="pcoa.acc.all.pdf")
```

```{r stats acc - site}
#seq.acc <- data.frame(otu_table(ps.acc))
ps.acc.rel <- transform_sample_counts(ps.acc, function(x) x / sum(x))
seq.acc <- data.frame(otu_table(ps.acc.rel))

dist.acc <- vegdist(seq.acc)
samdf.acc <- data.frame(sample_data(ps.acc))
row.names(samdf.acc)==row.names(seq.acc)

bet.all <- betadisper(dist.acc,samdf.acc$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.acc,samdf.acc$site)
#anova(bet.all)
permutest(bet.all, pairwise = TRUE, permutations = 999) #no diff in disp
plot(bet.all) 

adonis(seq.acc ~ site, data=samdf.acc, permutations=999)
adonis(seq.acc ~ site/zone, data=samdf.acc, permutations=999)
adonis(seq.acc ~ zone, strata=samdf.acc$site,data=samdf.acc, permutations=999)

pairwise.adonis(seq.acc, factors = samdf.acc$site, permutations = 999) #p < 0.001***
#        pairs  F.Model         R2 p.value p.adjusted
# 1 MNW vs MSE 5.881318 0.09206633   0.001      0.001
# 2 MNW vs TNW 3.194025 0.05054315   0.001      0.001
# 3 MSE vs TNW 3.745959 0.05876386   0.001      0.001
```

```{r acc by zone}
#by site
ps.acc.mnw <- subset_samples(ps.acc,site=="MNW")
ps.acc.mse <- subset_samples(ps.acc,site=="MSE")
ps.acc.tnw <- subset_samples(ps.acc,site=="TNW")

gg.pcoa.acc.mnw <- plot_ordination(ps.acc.mnw,ordinate(ps.acc.mnw,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))

gg.pcoa.acc.mse <- plot_ordination(ps.acc.mse,ordinate(ps.acc.mse,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))

gg.pcoa.acc.tnw <- plot_ordination(ps.acc.tnw,ordinate(ps.acc.tnw,"PCoA", "bray"),color="zone", shape="zone")+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))

ggarrange(gg.pcoa.acc.mnw,gg.pcoa.acc.mse,gg.pcoa.acc.tnw,nrow=1,common.legend=T,legend="right")
#ggsave("pcoa.acc.zone.pdf",width=11,height=3)



#### by site - MNW ####
seq.acc.mnw <- data.frame(otu_table(ps.acc.mnw))

dist.acc.mnw <- vegdist(seq.acc.mnw)
samdf.acc.mnw <- data.frame(sample_data(ps.acc.mnw))
row.names(samdf.acc.mnw)==row.names(seq.acc.mnw)

bet.all <- betadisper(dist.acc.mnw,samdf.acc.mnw$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

adonis(seq.acc.mnw ~ zone,data=samdf.acc.mnw, permutations=999)
# Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# zone       1    0.7993 0.79929  2.1125 0.07514  0.002 **
# Residuals 26    9.8374 0.37836         0.92486          
# Total     27   10.6367                 1.00000          
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#### by site - MSE ####
seq.acc.mse <- data.frame(otu_table(ps.acc.mse))

dist.acc.mse <- vegdist(seq.acc.mse)
samdf.acc.mse <- data.frame(sample_data(ps.acc.mse))
row.names(samdf.acc.mse)==row.names(seq.acc.mse)

bet.all <- betadisper(dist.acc.mse,samdf.acc.mse$zone)
anova(bet.all)
plot(bet.all) 
# Df   Sum Sq   Mean Sq F value  Pr(>F)  
# Groups     1 0.021763 0.0217633  4.5724 0.04169 *
# Residuals 27 0.128513 0.0047597                  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

adonis(seq.acc.mse ~ zone,data=samdf.acc.mse, permutations=999)
# Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# zone       1    0.8113 0.81126  2.2489 0.07689  0.004 **
# Residuals 27    9.7400 0.36074         0.92311          
# Total     28   10.5513                 1.00000 

#### by site - TNW ####
seq.acc.tnw <- data.frame(otu_table(ps.acc.tnw))

dist.acc.tnw <- vegdist(seq.acc.tnw)
samdf.acc.tnw <- data.frame(sample_data(ps.acc.tnw))
row.names(samdf.acc.tnw)==row.names(seq.acc.tnw)

bet.all <- betadisper(dist.acc.tnw,samdf.acc.tnw$zone)
anova(bet.all)
plot(bet.all) #ns                

adonis(seq.acc.tnw ~ zone,data=samdf.acc.tnw, permutations=999)
#  Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# zone       1    0.8429 0.84287  2.2735 0.08336  0.002 **
# Residuals 25    9.2685 0.37074         0.91664          
# Total     26   10.1113                 1.00000          
```

# Bar plots [needs fixing] {.tabset}

## All, by Phylum

```{r bar plot, eval=FALSE}
# ps.sz <- merge_samples(ps.rare.trim, "site_zone")
# ps.rel.sz <- transform_sample_counts(ps.sz, function(x) x / sum(x))
# plot_bar(ps.rel.sz, fill="Class")+
#   geom_bar(stat="identity")

ps.all.tab <- psmelt(ps.rare.trim)%>%
  filter(!is.na(Abundance))%>%
  group_by(site,zone,site_zone,Phylum,OTU)%>%
  summarize_at("Abundance",mean)

ps.all.tab$site[ps.all.tab$site == "MNW"] <- "Mo'orea NW"
ps.all.tab$site[ps.all.tab$site == "MSE"] <- "Mo'orea SE"
ps.all.tab$site[ps.all.tab$site == "TNW"] <- "Tahiti NW"

ps.all.tab$zone[ps.all.tab$zone == "Forereef"] <- "FR"
ps.all.tab$zone[ps.all.tab$zone == "Backreef"] <- "BR"

gg.bar.all.phy <- ggplot(ps.all.tab,aes(x=zone,y=Abundance,fill=Phylum))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_wrap(~site)

gg.bar.all.phy
#ggsave(gg.bar.all,file="bac.bar.all.pdf",height=4)
```

```{r, eval=FALSE}
pa <- psmelt(ps.all)
tb <- psmelt(ps.all)%>%
  filter(!is.na(Abundance))%>%
  group_by(site,zone,site_zone,Class,OTU)%>%
  summarize_at("Abundance",mean)

tb$zone <- gsub("out","FR",tb$zone)
tb$zone <- gsub("in","BR",tb$zone)

tb$site <- gsub("MNW","Mo'orea NW",tb$site)
tb$site <- gsub("MSE","Mo'orea SE",tb$site)
tb$site <- gsub("TNW","Tahiti NW",tb$site)

quartz()
ggplot(tb,aes(x=zone,y=Abundance,fill=Class))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_wrap(~site)
```

## All, by Class

```{r bar plot Class}
ps.sz <- merge_samples(ps.rare.trim, "site_zone")
ps.rel.sz <- transform_sample_counts(ps.sz, function(x) x / sum(x))
ps.rel.sz@sam_data$site <- c("a","b","c","a","b","c")
ps.rel.sz@sam_data$zone <- c("a","b","c","a","b","c")
plot_bar(ps.rel.sz,fill="Class")+
  geom_bar(stat="identity")+
  facet_wrap(~site*zone)

ps.all.tab <- psmelt(ps.rare.trim)%>%
  filter(!is.na(Abundance))%>%
  group_by(site,zone,site_zone,Class,OTU)%>%
  summarize_at("Abundance",mean)

ps.all.tab$site[ps.all.tab$site == "MNW"] <- "Mo'orea NW"
ps.all.tab$site[ps.all.tab$site == "MSE"] <- "Mo'orea SE"
ps.all.tab$site[ps.all.tab$site == "TNW"] <- "Tahiti NW"

ps.all.tab$zone[ps.all.tab$zone == "Forereef"] <- "FR"
ps.all.tab$zone[ps.all.tab$zone == "Backreef"] <- "BR"

gg.bar.all.cla <- ggplot(ps.all.tab,aes(x=zone,y=Abundance,fill=Class))+
  geom_bar(stat="identity")+
  theme_cowplot()+
  #theme(legend.position="none")+
  xlab('Reef zone')+  
  facet_wrap(~site)

gg.bar.all.cla
#ggsave(gg.bar.all,file="bac.bar.all.pdf",height=4)
```

# PCOA plots

## Plots - site {.tabset}

### Rarefied

```{r site rarefied}
ord <- ordinate(ps.rare.trim, "PCoA", "bray")
gg.pcoa.site.rare <- plot_ordination(ps.rare.trim, ord,color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))#+
  #xlab("Axis 1 (42.6%)")+
  #ylab("Axis 2 (24.1%)")+
  #ggtitle("Rarefied")
gg.pcoa.site.rare

ggsave("gg.bac.all.rare.site.pdf",width=5)
```

Stats

Help on adonis (here)[https://thebiobucket.blogspot.com/2011/04/assumptions-for-permanova-with-adonis.html#more]

```{r stats site rare}
seq.rare <- data.frame(otu_table(ps.rare.trim))

dist.rare <- vegdist(seq.rare)
samdf.rare <- data.frame(sample_data(ps.rare.trim))
row.names(samdf.rare)==row.names(seq.rare)

bet.all <- betadisper(dist.rare,samdf.rare$zone)
anova(bet.all)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.rare,samdf.rare$site)
permutest(bet.all, pairwise = TRUE, permutations = 999)
# Pairwise comparisons:
# (Observed p-value below diagonal, permuted p-value above diagonal)
#          MNW      MSE   TNW
# MNW          0.342000 0.215
# MSE 0.359986          0.045
# TNW 0.203563 0.049289     
plot(bet.all) #disp sig between MSE & TNW

adonis(seq.rare ~ site, data=samdf.rare, permutations=999)
adonis(seq.rare ~ site/zone, data=samdf.rare, permutations=999)
adonis(seq.rare ~ zone, strata=samdf.rare$site,data=samdf.rare, permutations=999)

pairwise.adonis(seq.rare, factors = samdf.rare$site, permutations = 999)
#       pairs  F.Model         R2 p.value p.adjusted
# 1 MNW vs MSE 3.863638 0.06563709   0.005      0.005
# 2 MNW vs TNW 2.474825 0.04461168   0.034      0.034
# 3 MSE vs TNW 6.216217 0.10323162   0.001      0.001
```

### Relative abundance

```{r sites rel abun}
ps.trim.rel <- transform_sample_counts(ps.trim, function(x) x / sum(x))
ord.rel <- ordinate(ps.trim.rel, "PCoA", "bray")
gg.pcoa.site <- plot_ordination(ps.trim.rel, ord.rel,color="site", shape="site")+
  stat_ellipse()+
  theme_cowplot()+
  scale_color_manual(name="Site",values=c("darkslategray3","darkslategray4","#000004"))+
  scale_shape_manual(name="Site",values=c(8,4,9))+
  xlab("Axis 1 (44.1%)")+
  ylab("Axis 2 (23%)")+
  ggtitle("Relative abundance")
gg.pcoa.site
```

Stats

```{r stats site rel}
seq.trim <- data.frame(otu_table(ps.trim.rel))

dist.trim <- vegdist(seq.trim)
samdf.trim <- data.frame(sample_data(ps.trim))
row.names(samdf.trim)==row.names(seq.trim)

bet.all <- betadisper(dist.trim,samdf.trim$zone)
anova(bet.all)
#permutest(bet.all, pairwise = FALSE, permutations = 999)
plot(bet.all) #very much overlap, not sig

bet.all <- betadisper(dist.trim,samdf.trim$site)
#anova(bet.all)
permutest(bet.all, pairwise = TRUE, permutations = 999)
plot(bet.all) #disp sig between MSE & TNW, same as rarefied
# Pairwise comparisons:
# (Observed p-value below diagonal, permuted p-value above diagonal)
#          MNW      MSE   TNW
# MNW          0.235000 0.164
# MSE 0.226153          0.019
# TNW 0.151332 0.014949      

adonis(seq.trim ~ site, data=samdf.trim, permutations=999)
adonis(seq.trim ~ site/zone, data=samdf.trim, permutations=999)
adonis(seq.trim ~ zone, strata=samdf.trim$site,data=samdf.trim, permutations=999)

pairwise.adonis(seq.trim, factors = samdf.trim$site, permutations = 999)
#all significantly different
#        pairs  F.Model         R2 p.value p.adjusted
# 1 MNW vs MSE 4.059614 0.06541475   0.005      0.005
# 2 MNW vs TNW 2.631393 0.04201397   0.031      0.031
# 3 MSE vs TNW 7.077436 0.10551142   0.001      0.001
```

### Plot - both

They look super similar

```{r ggarrange pcoas}
ggarrange(gg.pcoa.site.rare,gg.pcoa.site,labels="AUTO",common.legend=TRUE,legend="right")
```

## Plots - reef zones{.tabset} 

```{r subset data}
ps.mnw.rel <- subset_samples(ps.trim.rel,site=="MNW")
ps.mnw <- subset_samples(ps.rare.trim,site=="MNW")

ps.mse.rel <- subset_samples(ps.trim.rel,site=="MSE")
ps.mse <- subset_samples(ps.rare.trim,site=="MSE")

ps.tnw.rel <- subset_samples(ps.trim.rel,site=="TNW")
ps.tnw <- subset_samples(ps.rare.trim,site=="TNW")
```

### Mo'orea NW

Relative abundance - appears total overlap

```{r mnw rel}
ord.mnw.rel <- ordinate(ps.mnw.rel, "PCoA", "bray")
gg.mnw.rel <- plot_ordination(ps.mnw.rel, ord.mnw.rel,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea NW")+
  xlab("Axis 1 (38.8%)")+
  ylab("Axis 2 (29.8%)")+
  theme(axis.text=element_text(size=10))
gg.mnw.rel
```

Stats

```{r stats mnw rel}
seq.mnw.rel <- data.frame(otu_table(ps.mnw.rel))
samdf.mnw.rel <- data.frame(sample_data(ps.mnw.rel))
row.names(samdf.mnw.rel)==row.names(seq.mnw.rel)

dist.mnw.rel <- vegdist(seq.mnw.rel)
bet.mnw.rel <- betadisper(dist.mnw.rel,samdf.mnw.rel$zone,bias.adjust = TRUE,type="median")
anova(bet.mnw.rel) #not sig
#permutest(bet.mnw.rel, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mnw.rel)

adonis(seq.mnw.rel ~ zone, data=samdf.mnw.rel, permutations=999) #not sig
```

Rarefied

Slightly less overlap - but maybe still non-significant? 

```{r mnw rare}
ord.mnw <- ordinate(ps.mnw, "PCoA", "bray")
gg.mnw <- plot_ordination(ps.mnw, ord.mnw,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea NW")+
  xlab("Axis 1 (38.9%)")+
  ylab("Axis 2 (30.4%)")+
  theme(axis.text=element_text(size=10))
gg.mnw
```

Stats

```{r stats mnw rare}
seq.mnw.rare <- data.frame(otu_table(ps.mnw))
samdf.mnw.rare <- data.frame(sample_data(ps.mnw))
row.names(samdf.mnw.rare)==row.names(seq.mnw.rare)

dist.mnw.rare <- vegdist(seq.mnw.rare)
bet.mnw.rare <- betadisper(dist.mnw.rare,samdf.mnw.rare$zone,bias.adjust = TRUE,type="median")
anova(bet.mnw.rare) #not sig
#permutest(bet.mnw.rare, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mnw.rare)

adonis(seq.mnw.rare ~ zone, data=samdf.mnw.rare, permutations=999) #not sig
```

### Mo'orea SE

Relative abundance - appears to separate more than MNW

```{r mse rel}
ord.mse.rel <- ordinate(ps.mse.rel, "PCoA", "bray")
gg.mse.rel <- plot_ordination(ps.mse.rel, ord.mse.rel,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea SE")+
  xlab("Axis 1 (39.6%)")+
  ylab("Axis 2 (27.2%)")+
  theme(axis.text=element_text(size=10))
gg.mse.rel
```

Stats

```{r stats mse rel}
seq.mse.rel <- data.frame(otu_table(ps.mse.rel))
samdf.mse.rel <- data.frame(sample_data(ps.mse.rel))
row.names(samdf.mse.rel)==row.names(seq.mse.rel)

dist.mse.rel <- vegdist(seq.mse.rel)
bet.mse.rel <- betadisper(dist.mse.rel,samdf.mse.rel$zone,bias.adjust = TRUE,type="median")
anova(bet.mse.rel) #not sig
#permutest(bet.mse.rel, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mse.rel)

adonis(seq.mse.rel ~ zone, data=samdf.mse.rel, permutations=999) #p < 0.01**
```

Rarefied

Equivalent

```{r mse rare}
ord.mse <- ordinate(ps.mse, "PCoA", "bray")
gg.mse <- plot_ordination(ps.mse, ord.mse,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Mo'orea SE")+
  xlab("Axis 1 (38.1%)")+
  ylab("Axis 2 (27.8%)")+
  theme(axis.text=element_text(size=10))
gg.mse
```

Stats

Same story

```{r stats mse rare}
seq.mse.rare <- data.frame(otu_table(ps.mse))
samdf.mse.rare <- data.frame(sample_data(ps.mse))
row.names(samdf.mse.rare)==row.names(seq.mse.rare)

dist.mse.rare <- vegdist(seq.mse.rare)
bet.mse.rare <- betadisper(dist.mse.rare,samdf.mse.rare$zone,bias.adjust = TRUE,type="median")
anova(bet.mse.rare) #not sig
#permutest(bet.mse.rare, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.mse.rare)

adonis(seq.mse.rare ~ zone, data=samdf.mse.rare, permutations=999) #p < 0.01**
```

### Tahiti NW

Relative abundance - looks very silly

```{r tnw rel}
ord.tnw.rel <- ordinate(ps.tnw.rel, "PCoA", "bray")
gg.tnw.rel <- plot_ordination(ps.tnw.rel, ord.tnw.rel,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("Back reef","Fore reef"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Tahiti NW")+
  #xlab("Axis 1 (60.2%)")+
  #ylab("Axis 2 (9.7%)")+
  theme(axis.text=element_text(size=10))
gg.tnw.rel
```

Stats

```{r stats tnw rel}
seq.tnw.rel <- data.frame(otu_table(ps.tnw.rel))
samdf.tnw.rel <- data.frame(sample_data(ps.tnw.rel))
row.names(samdf.tnw.rel)==row.names(seq.tnw.rel)

dist.tnw.rel <- vegdist(seq.tnw.rel)
bet.tnw.rel <- betadisper(dist.tnw.rel,samdf.tnw.rel$zone,bias.adjust = TRUE,type="median")
anova(bet.tnw.rel) #p < 0.05*
#permutest(bet.tnw.rel, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.tnw.rel)

adonis(seq.tnw.rel ~ zone, data=samdf.tnw.rel, permutations=999) #p < 0.01**
```

Rarefied

Equivalent

```{r tnw rare}
ord.tnw <- ordinate(ps.tnw, "PCoA", "bray")
gg.tnw <- plot_ordination(ps.tnw, ord.tnw,color="zone", shape="zone")+
  geom_point(size=2)+
  stat_ellipse()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("BR","FR"))+
  guides(color=guide_legend(title="Reef zone"),shape=guide_legend(title="Reef zone"))+
  ggtitle("Tahiti NW")+
  xlab("Axis 1 (59.4%)")+
  ylab("Axis 2 (10.8%)")+
  theme(axis.text=element_text(size=10))
gg.tnw
```

Stats

```{r stats tnw rare}
seq.tnw.rare <- data.frame(otu_table(ps.tnw))
samdf.tnw.rare <- data.frame(sample_data(ps.tnw))
row.names(samdf.tnw.rare)==row.names(seq.tnw.rare)

dist.tnw.rare <- vegdist(seq.tnw.rare)
bet.tnw.rare <- betadisper(dist.tnw.rare,samdf.tnw.rare$zone,bias.adjust = TRUE,type="median")
anova(bet.tnw.rare) #p < 0.01**
permutest(bet.tnw.rare, pairwise = FALSE, permutations = 999) #says the same thing
plot(bet.tnw.rare)

adonis(seq.tnw.rare ~ zone, data=samdf.tnw.rare, permutations=999) #p < 0.01**
```

## Summary

- No differences in results between relative abundance & rarefied plots/stats
- Pairwise adonis significant between all three sites
- Adonis significant across reef zones at TNW & MSE, but not MNW
- Beta dispersion not significantly different except between TNW F & B (can definitely see it)

Relative abundance

```{r panels rel}
ggarrange(gg.mnw.rel,gg.mse.rel,gg.tnw.rel,nrow=1,common.legend=TRUE,legend="right",labels="AUTO")
```

Rarefied

```{r panels rare}
ggarrange(gg.mnw,gg.mse,gg.tnw,nrow=1,common.legend=TRUE,legend="right",labels=c("(a)","(b)","(c)"))
#ggsave("16s.pcoa.pdf",height=2.5,width=8)
```

# ANCOM

Tutorial [here](https://github.com/FrederickHuangLin/ANCOM)

## Setup

```{r ancom packages}
library(readr)
library(tidyverse)
#library(dplyr)
library(nlme)
#install.packages('compositions')
library(compositions)
source("ancom_v2.1.R")

#setwd("/Volumes/GoogleDrive/My Drive/Moorea_revisions/mr16s_revised/analysis/03.community_comp")
```

```{r ancom all, eval=FALSE}
otu_data_unt <- data.frame(ps.trim@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.trim@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = "~ 1 | site"

res.all = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.mnw,file="ancom.res.mnw.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.all$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.all$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

## ANCOM by site{.tabset}

Note: shouldn't be done on rarefied according to authors

Ran these three chunks once, then loading in data below

### MNW

```{r ancom mnw, eval=FALSE}
ps.mnw <- subset_samples(ps.trim,site=="MNW")

otu_data_unt <- data.frame(ps.mnw@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.mnw@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = NULL

res.mnw = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.mnw,file="ancom.res.mnw.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.mnw$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.mnw$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

### MSE

```{r ancom mse, eval=FALSE}
ps.mse <- subset_samples(ps.trim,site=="MSE")

otu_data_unt <- data.frame(ps.mse@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.mse@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = NULL

res.mse = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.mse,file="ancom.res.mse.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.mse$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.mse$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

### TNW

```{r ancom tnw, eval=FALSE}
ps.tnw <- subset_samples(ps.trim,site=="TNW")

otu_data_unt <- data.frame(ps.tnw@otu_table)
otu_data<- data.frame(t(otu_data_unt))
#might need to make the sample names an actual row yet, not sure

meta_data = data.frame(ps.tnw@sam_data)
meta_data = meta_data %>% rename(Sample.ID = id)

# Step 1: Data preprocessing

feature_table = otu_data; sample_var = "Sample.ID"; group_var = NULL
out_cut = 0.05; zero_cut = 0.90; lib_cut = 1000; neg_lb = FALSE
prepro = feature_table_pre_process(feature_table, meta_data, sample_var, group_var, 
                                   out_cut, zero_cut, lib_cut, neg_lb)
feature_table = prepro$feature_table # Preprocessed feature table
meta_data = prepro$meta_data # Preprocessed metadata
struc_zero = prepro$structure_zeros # Structural zero info

# Step 2: ANCOM

main_var = "zone"; p_adj_method = "BH"; alpha = 0.05
adj_formula = NULL; rand_formula = NULL

res.tnw = ANCOM(feature_table, meta_data, struc_zero, main_var, p_adj_method, 
            alpha, adj_formula, rand_formula)

#saveRDS(res.tnw,file="ancom.res.tnw.RDS")

# Step 3: Volcano Plot

# Number of taxa except structural zeros
n_taxa = ifelse(is.null(struc_zero), nrow(feature_table), sum(apply(struc_zero, 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = c(0.9 * (n_taxa -1), 0.8 * (n_taxa -1), 0.7 * (n_taxa -1), 0.6 * (n_taxa -1))
names(cut_off) = c("detected_0.9", "detected_0.8", "detected_0.7", "detected_0.6")

# Annotation data
dat_ann = data.frame(x = min(res.tnw$fig$data$x), y = cut_off["detected_0.7"], label = "W[0.7]")

fig = res.tnw$fig +  
  geom_hline(yintercept = cut_off["detected_0.7"], linetype = "dashed") + 
  geom_text(data = dat_ann, aes(x = x, y = y, label = label), 
            size = 4, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE)
fig  
```

## Synthesizing ANCOM results

Re-read in data

```{r load ancom results}
res.mnw <- readRDS("ancom.res.mnw.RDS")
res.mse <- readRDS("ancom.res.mse.RDS")
res.tnw <- readRDS("ancom.res.tnw.RDS")
```

Which ones are 'significant'

```{r subset out files}
mnw.out <- res.mnw$out
mnw.out.sig <- mnw.out[mnw.out$detected_0.6==TRUE,]
#1

mse.out <- res.mse$out
mse.out.sig <- mse.out[mse.out$detected_0.6==TRUE,]
#8

tnw.out <- res.tnw$out
tnw.out.sig <- tnw.out[tnw.out$detected_0.6==TRUE,]
#4
```

Subset the sig ones in phyloseq

```{r}
want.mnw <- c(mnw.out.sig$taxa_id)
want.mse <- c(mse.out.sig$taxa_id)
want.tnw <- c(tnw.out.sig$taxa_id)

want <- c(want.mnw,want.mse,want.tnw)

ps.sig.taxa <- subset_taxa(ps.rare.trim,row.names(ps.trim@tax_table) %in% want)
#37 & 13 are in there twice

#looks so cool!
plot_bar(ps.sig.taxa,x="site_zone",y="Abundance",fill="Genus")+
  facet_wrap(~Genus,scales="free")

#ggsave("sig.genus.abun.pdf",width=11)
```



