---
title: "Environmental data"
author: "Nicola G. Kriefall"
date: "6/30/2021"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
    #code_folding: hide
---

```{r setup, include=FALSE}
#work computer 
#setwd("~/nicfall@bu.edu - Google Drive/My Drive/Moorea_revisions/env_revised")
#home computer
#setwd("/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/")
```

## Setup - load packages

```{r packages}
library(ggplot2)
library(cowplot)
library(dplyr)
library(colorBlindness)
library(scales)
library(bestNormalize)
library(Rmisc)
library(ggpubr)
```

# Substrate composition

```{r data processing}
#home comp
sub.tah <- read.csv('/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/substrate.csv',header=TRUE)
#work comp
#sub.tah <- read.csv('~/nicfall@bu.edu - Google Drive/My Drive/Moorea_revisions/env_revised/substrate.csv',header=TRUE)

sub <- subset(sub.tah,Marine.Area!="Tahiti Faaa")

sub$Substrate <- as.factor(sub$Substrate)
#str(sub)
##total proportion
sub$prop.test <- (sub$proportion)/3

##rename sites & habitats
sub$Marine.Area <- as.factor(sub$Marine.Area)
levels(sub$Marine.Area)
levels(sub$Marine.Area) <- c("Mo'orea SE","Mo'orea NW")
levels(sub$Marine.Area)
sub$Marine.Area <- factor(sub$Marine.Area, levels=c("Mo'orea NW","Mo'orea SE")) #reorder

sub$Habitat <- as.factor(sub$Habitat)
levels(sub$Habitat)
levels(sub$Habitat) <- c("Back","Fore")
levels(sub$Habitat)

##only interested in 2013 - year of collection
sub13 <- subset(sub,Year=="2013")
sub14 <- subset(sub,Year=="2014")
```

## Plots {.tabset}

### Figure - all the categories

```{r plot2}
ggplot(data=sub13, aes(x=Habitat, y=prop.test, fill=Substrate)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')

ggplot(data=sub14, aes(x=Habitat, y=prop.test, fill=Substrate)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')

#ggsave("substrate.png")
```

### Figure - summed categories

```{r plot summed cats}
sub13$Substrate <- gsub(" ","_",sub13$Substrate)

sub13$sub_cats <- recode(sub13$Substrate, Acropora="Coral", Asparagopsis="Algae", Cyanophyceae="Algae", Dead_coral="Abiotic substrata", Dictyota="Algae", Halimeda="Algae", Macroalgae="Algae", Millepora="Coral", Montastrea="Coral", Montipora="Coral", Napopora="Coral", Pavement="Abiotic substrata", Pavona="Coral", Pocillopora="Coral", Porites="Coral", Psammocora="Coral", Rubble="Abiotic substrata", Sand="Abiotic substrata", Stegastes_Turf="Algae", Synarea="Coral", Turbinaria="Coral")

pal <- hcl.colors(12,"Tofino")
show_col(pal)
colorz <- c("#3B415E","#8FC67C","#818CC0")

sub3 <- ggplot(data=sub13, aes(x=Habitat, y=prop.test, fill=sub_cats)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
  scale_fill_manual(values=colorz,name="Substrate",labels=c("Abiotic","Algae","Coral"))

sub3

#cvdPlot(sub3)

#ggsave("substrate_3cats.png",height=3.5) #can also go back to default if square

sub14$Substrate <- gsub(" ","_",sub14$Substrate)

sub14$sub_cats <- recode(sub14$Substrate, Acropora="Coral", Asparagopsis="Algae", Cyanophyceae="Algae", Dead_coral="Abiotic substrata", Dictyota="Algae", Halimeda="Algae", Macroalgae="Algae", Millepora="Coral", Montastrea="Coral", Montipora="Coral", Napopora="Coral", Pavement="Abiotic substrata", Pavona="Coral", Pocillopora="Coral", Porites="Coral", Psammocora="Coral", Rubble="Abiotic substrata", Sand="Abiotic substrata", Stegastes_Turf="Algae", Synarea="Coral", Turbinaria="Coral")

pal <- hcl.colors(12,"Tofino")
show_col(pal)
colorz <- c("#3B415E","#8FC67C","#818CC0")

sub4 <- ggplot(data=sub14, aes(x=Habitat, y=prop.test, fill=sub_cats)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
  scale_fill_manual(values=colorz,name="Substrate",labels=c("Abiotic","Algae","Coral"))

sub4
```

### Figure - medium categories

```{r medium categories}
sub13$sub_cats_med <- recode(sub13$Substrate, Acropora="Coral - Acropora", Asparagopsis="Algae - Asparagopsis", Cyanophyceae="Algae - Cyanophyceae", Dead_coral="Abiotic (e.g. rubble, sand)", Dictyota="Algae - Dictyota", Halimeda="Algae - Halimeda", Macroalgae="Algae - Macroalgae", Millepora="Coral - Millepora", Montastrea="Coral - Montastrea", Montipora="Coral - Montipora", Napopora="Coral - Napopora", Pavement="Abiotic (e.g. rubble, sand)", Pavona="Coral - Pavona", Pocillopora="Coral - Pocillopora", Porites="Coral - Porites", Psammocora="Coral - Psammocora", Rubble="Abiotic (e.g. rubble, sand)", Sand="Abiotic (e.g. rubble, sand)", Stegastes_Turf="Algae - Stegastes Turf", Synarea="Coral - Synarea", Turbinaria="Coral - Turbinaria")  

#greens for algae
#pal.gr <- hcl.colors(5,"Greens")
#show_col(pal.gr)
#pal.gr
#"#004616" "#30893B" "#81C07A" "#CAE8C1" "#F6FBF4"
#pal.bl <- hcl.colors(9,"BuPu")
#show_col(pal.bl)
#pal.bl
#"#540046" "#6E2072" "#8346A1" "#8674B8" "#9099CA" "#A3BAD9" "#BED6E6" "#DBECF3" "#F2FBFC"

colorz2 <- c("grey","#004616","#30893B","#81C07A","#CAE8C1","#F6FBF4","#540046","#6E2072","#8346A1","#8674B8","#9099CA","#A3BAD9","#BED6E6","#DBECF3","#F2FBFC")

sub.med <- ggplot(data=sub13, aes(x=Habitat, y=prop.test, fill=sub_cats_med)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
 scale_fill_manual(values=colorz2,name="Substrate")

sub.med
#ggsave("substrate_medcats.png",height=4) #can also go back to default if square
#cvdPlot(sub.med)

sub14$sub_cats_med <- recode(sub14$Substrate, Acropora="Coral - Acropora", Asparagopsis="Algae - Asparagopsis", Cyanophyceae="Algae - Cyanophyceae", Dead_coral="Abiotic (e.g. rubble, sand)", Dictyota="Algae - Dictyota", Halimeda="Algae - Halimeda", Macroalgae="Algae - Macroalgae", Millepora="Coral - Millepora", Montastrea="Coral - Montastrea", Montipora="Coral - Montipora", Napopora="Coral - Napopora", Pavement="Abiotic (e.g. rubble, sand)", Pavona="Coral - Pavona", Pocillopora="Coral - Pocillopora", Porites="Coral - Porites", Psammocora="Coral - Psammocora", Rubble="Abiotic (e.g. rubble, sand)", Sand="Abiotic (e.g. rubble, sand)", Stegastes_Turf="Algae - Stegastes Turf", Synarea="Coral - Synarea", Turbinaria="Coral - Turbinaria")  

#greens for algae
pal.gr <- hcl.colors(5,"Greens")
show_col(pal.gr)
pal.gr
#"#004616" "#30893B" "#81C07A" "#CAE8C1" "#F6FBF4"
pal.bl <- hcl.colors(9,"BuPu")
show_col(pal.bl)
pal.bl
#"#540046" "#6E2072" "#8346A1" "#8674B8" "#9099CA" "#A3BAD9" "#BED6E6" "#DBECF3" "#F2FBFC"

colorz2 <- c("grey","#004616","#30893B","#81C07A","#CAE8C1","#F6FBF4","#540046","#6E2072","#8346A1","#8674B8","#9099CA","#A3BAD9","#BED6E6","#DBECF3","#F2FBFC")

sub.med2 <- ggplot(data=sub14, aes(x=Habitat, y=prop.test, fill=sub_cats_med)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
 scale_fill_manual(values=colorz2,name="Substrate")

sub.med2
#ggsave("substrate_medcats.png",height=4) #can also go back to default if square
#cvdPlot(sub.med)
```

## Synthesizing

```{r}
ggarrange(sub.med,sub.med2,common.legend=TRUE,legend="right")
```

```{r, eval=FALSE, include=FALSE}
#Tahiti didn't really work

# tah <- subset(sub.tah,Marine.Area=="Tahiti Faaa")
# 
# tah$Substrate <- gsub(" ","_",tah$Substrate)
# 
# tah$sub_cats <- recode(tah$Substrate, Acropora="Coral", Montipora="Coral", Pavona="Coral", Pocillopora="Coral", Porites="Coral", Astrea_curta="Coral", Leptastrea="Coral", Autres="Coral")  
# 
# tah$sub_cats_med <- recode(tah$Substrate, Acropora="Coral - Acropora", Montipora="Coral - Montipora", Pavona="Coral - Pavona", Pocillopora="Coral - Pocillopora", Porites="Coral - Porites", Astrea_curta="Coral - Astrea curta", Leptastrea="Coral - Leptastrea", Autres="Coral - Autres")  
# 
# sub.coral <- subset(sub13,sub_cats=="Coral")
# 
# tah$prop.test <- (tah$proportion)/20
# 
# corals <- rbind(tah,sub.coral)
# 
# ggplot(data=corals, aes(x=Habitat, y=prop.test, fill=Substrate)) +
#   geom_bar(stat="identity")+
#   facet_wrap(~Marine.Area)+
#   theme_cowplot()+
#   ylab('Relative proportion')+
#   xlab('Reef zone')                    
```

# Nutrients

```{r read in nutrient data}
#home comp
nuts <- read.csv("/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/nuts_13-14_renamed.csv",header=T)
#work comp
#nuts <- read.csv("~/nicfall@bu.edu - Google Drive/My Drive/Moorea_revisions/env_revised/nuts_13-14_renamed.csv",header=T)

str(nuts)
```

## From revisions - by month {.tabset}

### Phosphate revised

```{r}
nuts$ym <- paste0(nuts$year,"_",nuts$month)
nuts$date2 <- as.Date(nuts$date,"%m/%d/%y")

gg.new.pho <- ggplot(nuts,aes(x=date2,y=Phosphate_P2O5_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Phosphates (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.pho
```

### Nitrates revised

```{r}
gg.new.nia <- ggplot(nuts,aes(x=date2,y=Nitrates_NO3_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Nitrates (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.nia
```

### Nitrites revised

```{r}
gg.new.nii <- ggplot(nuts,aes(x=date2,y=Nitrites_NO2_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Nitrites (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.nii
```

### Silica revised

```{r}
gg.new.sil <- ggplot(nuts,aes(x=date2,y=Silice_SiO2_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Silica (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.sil
```

### Ammonium revised

```{r}
gg.new.amm <- ggplot(nuts,aes(x=date2,y=Ammonium_NH4_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Ammonium (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.amm
```

## Results summarized - revised

```{r multipanel revised}
ggarrange(gg.new.pho,gg.new.nia,gg.new.nii,gg.new.sil,gg.new.amm,labels="AUTO",common.legend=TRUE,legend="right",nrow=5)
#ggsave("env_nutrients_revised.pdf",height=12)
```

## Box plots

### Wrap by year

```{r box plots x year}
ggplot(nuts,aes(x=habitat,y=Phosphate_P2O5_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Nitrates_NO3_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Nitrites_NO2_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Silice_SiO2_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Ammonium_NH4_uM))+
  geom_boxplot()+
  facet_wrap(~year)
```

## Violin plots {.tabset}

### Phosphates

```{r violin phos}
gg.pho <- ggplot(nuts,aes(x=habitat,y=Phosphate_P2O5_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.7)+
  theme_cowplot()+
  geom_boxplot(width=0.1,alpha=0)+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Phosphates (µM)")
gg.pho

library(car)

nuts$habitat <- as.factor(nuts$habitat)
shapiro.test(log(nuts$Phosphate_P2O5_uM))
leveneTest(nuts$Phosphate_P2O5_uM,nuts$habitat)#ns

summary(aov(Phosphate_P2O5_uM~habitat,data=nuts)) #ns
#wilcox.test(Phosphate_P2O5_uM~habitat,data=nuts,exact=FALSE) #ns
```

### Nitrates

```{r violin nitra}
gg.nia <- ggplot(nuts,aes(x=habitat,y=Nitrates_NO3_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.7)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Nitrates (µM)")
gg.nia

shapiro.test(log(nuts$Nitrates_NO3_uM)) #no
leveneTest(nuts$Nitrates_NO3_uM,nuts$habitat)#ns

#summary(aov(Nitrates_NO3_uM~habitat,data=nuts)) #p < 0.01**
wilcox.test(Nitrates_NO3_uM~habitat,data=nuts,exact=FALSE) #p < 0.01**
# Wilcoxon rank sum test with continuity correction
# 
# data:  Nitrates_NO3_uM by habitat
# W = 435, p-value = 0.002519

sum.nia <- summarySE(data=nuts,measurevar="Nitrates_NO3_uM",groupvars="habitat")
sum.nia
```

### Nitrites

```{r violin nitrites}
gg.nii <- ggplot(nuts,aes(x=habitat,y=Nitrites_NO2_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.7)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Nitrites (µM)")
gg.nii

shapiro.test(nuts$Nitrites_NO2_uM)

#summary(aov(Nitrites_NO2_uM~habitat,data=nuts)) #p < 0.05*
wilcox.test(Nitrites_NO2_uM~habitat,data=nuts,exact=FALSE) #p < 0.01**

sum.nii <- summarySE(data=nuts,measurevar="Nitrites_NO2_uM",groupvars="habitat")
sum.nii
```

### Silica

```{r violin sili}
gg.sil <- ggplot(nuts,aes(x=habitat,y=Silice_SiO2_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.5)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Silica (µM)")
gg.sil
summary(aov(Silice_SiO2_uM~habitat,data=nuts)) #ns
wilcox.test(Silice_SiO2_uM~habitat,data=nuts) #ns
```

### Ammonium

```{r violin ammo}
gg.amm <- ggplot(nuts,aes(x=habitat,y=Ammonium_NH4_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.5)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Ammonium (µM)")
gg.amm
summary(aov(Ammonium_NH4_uM~habitat,data=nuts)) #ns
wilcox.test(Ammonium_NH4_uM~habitat,data=nuts) #ns
```

## Multipanel violin plot

Results: 
- phosphates not sig, log-transformed anova
- nitrates
- nitrites
- silica
- ammonium

```{r}
library(ggpubr)

ggarrange(gg.pho,gg.nia,gg.nii,gg.sil,gg.amm,labels="AUTO")
#ggsave("env_nutrients.pdf",width=7)

```

# Flow

```{r flow data}
#home comp
flowdat <- read.csv("/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/flow_rates_reformatted.csv",header=T)
#work comp
#flowdat <- read.csv("~/nicfall@bu.edu - Google Drive/My Drive/Moorea_revisions/env_revised/flow_rates_reformatted.csv",header=T)

ggplot(flowdat,aes(x=site,y=speed_ms,fill=site))+
  geom_boxplot()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Flow (m/s)")+
  xlab("Site-reef zone")+
  theme(legend.position="none")
#ggsave("mnw.flow.pdf",width=2.5,height=2)

best.speed <- bestNormalize(flowdat$speed_ms)
flowdat$speed.t <- best.speed$x.t

a.flow <- aov(speed.t~site,data=flowdat)
summary(a.flow)
plot(a.flow)

flow.sd <- summarySE(data=flowdat,measurevar="speed_ms",groupvars="site")
flow.sd
```

# Temperature

```{r temp packages}
library("ggplot2")
library("Rmisc")
#install.packages("lubridate")
#install.packages("tidyverse")
library("lubridate")
library("tidyverse")
library("cowplot")
library("ggpubr")
library("extrafont")
```

```{r}
#started with hogo logger excel sheets, 
#cleaned the header so R would be happy, 
#added the logger column,
#lastly duplicated the date/time column so that I could 
#have one each for 'year', 'month', 'day', and 'time'. 
#Designated these by changing the 'custom format' for the cells in Excel

#read in data
data <- read.csv("~/Google Drive (thenicolakriefall@gmail.com)/Moorea/Fig_env/mr_env.csv",header=TRUE)
str(data$site)

#me trying to get R to understand my date formatting
data$date <- paste(data$year,"/",data$month,"/",data$day)
data$date <- gsub(' ', '', data$date)
data$date <- as.Date(data$date,format="%Y/%m/%d")

#examining individual sites
# f1 <- subset(data,site=="F1") #closest to shore, fringing reef
# c <- subset(data,site=="C") #channel
b1 <- subset(data,site=="B1") #barrier reef
p3 <- subset(data,site=="P3") #outer slope
# p8 <- subset(data,site=="P8") #next outer slope
# p14 <- subset(data,site=="P14") 
# p25 <- subset(data,site=="P25")
# p35 <- subset(data,site=="P35")
# p55 <- subset(data,site=="P55")

#checking them out
plot(temp~date,data=p3)

#plotting all of them
ggplot(data,aes(x=date,y=temp,group=site,color=site))+
  geom_line()

#lots of strange noise in the deeper sites in the middle, taking those out:
noise <- subset(data,site=="C" | site =="F1" | site=="B1" | site=="P3" | site=="P8")
noise$site <- factor(noise$site,levels=c("F1","B1","C","P3","P8"))
ggplot(noise,aes(x=date,y=temp,group=site,color=site))+
  geom_line()

#most interested in B1 barrier reef & P3
spec <- subset(data,site=="B1" | site=="P3")
ggplot(spec,aes(x=date,y=temp,group=site,color=site))+
  geom_line()+
  scale_color_manual(name="Reef zone",values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme_cowplot()+
  ylab("Temperature (˚C)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),text=element_text(family="Gill Sans MT"))

#plotting summer months because most interesting
spec2 <- spec %>%
  filter(as.Date(spec$date) >= as.Date("2013-06-01") & as.Date(spec$date) <= as.Date("2013-09-01"))

#install.packages("extrafont")
library(extrafont)
font_import()  # Import fonts
loadfonts()  # Load them all
fonts()  # See what fonts are available

colorz <- c("coral1","cyan3")
spec2$all <- paste(spec2$date,spec2$time)
ggplot(spec2,aes(x=all,y=temp,color=site,group=site))+
  geom_line()+
  ylab('Temperature (˚C)')+
  xlab('')+
  scale_color_manual(values=colorz,labels=c("Inshore","Offshore"))+
  theme_classic()+
  theme(legend.position=c(0.175,0.175),legend.background = element_rect(color=1),text=element_text(family="Gill Sans MT"))+
  scale_x_discrete(labels=c("Jun 2013","Jul 2013","Aug 2013"),breaks=c("2013-06-15 00:00","2013-07-15 00:00","2013-08-15 00:00"))+
  labs(color="Reef zone")

#all the year instead of just some
spec$all <- paste(spec$date,spec$time)
ggplot(spec,aes(x=date,y=temp,color=site,group=site))+
  geom_line()+
  ylab('Temperature (˚C)')+
  xlab('')+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Backreef","Forereef"))+
  theme_cowplot()+
  theme(legend.position=c(0.175,0.175),legend.background = element_rect(color=1),text=element_text(family="Gill Sans MT"))+
  scale_x_discrete(labels=c("Jun 2013","Jul 2013","Aug 2013"),breaks=c("2013-06-15 00:00","2013-07-15 00:00","2013-08-15 00:00"))+
  labs(color="Reef zone")

#Temperature by month boxplot
temp <- summarySE(spec,measurevar="temp",groupvars=c("site","month","observ"))
temp$month <- as.factor(temp$month)
ggplot(temp,aes(x=month,y=temp,color=site))+
  geom_boxplot()+
  theme_bw()

var.test(values ~ groups, data, 
         alternative = "two.sided")

#install.packages("doBy")
library("doBy") 
#citation("doBy")
#citation("ggplot2")
#defining functions to do: mean, variance, and range (min & max)
fun <- function(x){
  c(m=mean(x), v=var(x), r=range(x))
}
range <- summaryBy(temp ~ date*site, data=spec,
                   FUN=fun)
str(range)
range$var <- range$temp.r2-range$temp.r1

svar <- summarySE(range,measurevar="var",groupvars="site",na.rm = TRUE)

svar
# site  N       var        sd         se         ci
# 1   B1 93 1.1800430 0.5167392 0.05358336 0.10642117
# 2   P8 93 0.3056022 0.1472730 0.01527150 0.03033051

#calculating some averages by site:
br <- subset(range,site=="B1")
fr <- subset(range,site=="P3")

mean(br$var) #0.9259726
sd(br$var) #0.4460952
mean(br$temp.r1) #27.12399
mean(br$temp.r2) #28.04996

mean(fr$var) #0.5052822
sd(fr$var) #0.2305518
mean(fr$temp.r1) #27.26698
mean(fr$temp.r2) #27.77226

#plotting range in temperature data by day
#old plot
var <- ggplot(svar,aes(x=site,y=var,color=site,shape=site))+
  geom_jitter(data=range,alpha=0.05)+
  geom_point()+
  geom_errorbar(aes(ymin=var-sd,ymax=var+sd),width=0.1)+
  theme_cowplot()+
  ylab("Temp. range (˚C/day)")+
  xlab("Site")+
  scale_x_discrete(breaks=c("B1","P3"),labels=c("MNW-B","MNW-F"))+
  theme(legend.position="none")+
  geom_text(x=2, y=2.9, label="p < 0.005***",color="black")+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_shape_manual(values=c(16,15))
var

#boxplot instead
var <- ggplot(range,aes(x=site,y=var,color=site,shape=site))+
  geom_jitter(alpha=0.5)+
  geom_boxplot(outlier.shape=NA,alpha=0.8)+
  theme_cowplot()+
  ylab("Temp. range (˚C/day)")+
  xlab("Site-RZ")+
  scale_x_discrete(breaks=c("B1","P3"),labels=c("MNW-B","MNW-F"))+
  theme(legend.position="none")+
  #geom_text(x=2, y=2.9, label="p < 0.001***",color="black")+
  annotate(geom="text", x=2, y=2.9, label="p < 0.001***")+
  scale_color_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_shape_manual(values=c(16,15))
var

#maybe density plot instead
ggplot(range,aes(x=var,color=site))+
  geom_density(data=range,alpha=0.2)

a1 <- aov(log(var)~site,data=range)
summary(a1)
par(mfrow=c(2,2))
plot(a1)
shapiro.test(log(range$var)) #normal

library(bestNormalize)
bestNormalize(range$temp.m)
norm <- orderNorm(range$temp.m)
range$temp.m.t <- norm$x.t
shapiro.test(range$temp.m.t) #doesn't work
a2 <- aov(temp.m.t~site,data=range)
summary(a2)
par(mfrow=c(2,2))
plot(a2)

wilcox.test(temp.m~site,data=range)
a2 <- aov(temp.m~site,data=range)
summary(a2)
par(mfrow=c(2,2))
plot(a2)

#justsite <- summaryBy(temp ~ site*time, data=spec3,
#                   FUN=fun)

#the average at the same time for the month of July
spec3 <- spec %>%
  filter(as.Date(spec$date) >= as.Date("2013-07-01") & as.Date(spec$date) <= as.Date("2013-08-01"))

#month <- summarySE(spec3,measurevar="temp",groupvars=c("site","time"),na.rm = TRUE)
ggplot(spec3,aes(x=time,y=temp,color=site,group=site))+
  geom_smooth(aes(color=site,group=site))+
  scale_x_discrete(breaks=c("01:00","12:00","22:00"),labels=c("1am","12pm","10pm"))+
  theme_cowplot()+
  xlab("Time")+
  ylab("Temperature (˚C)")+
  scale_color_manual(name="Site",values=c("#ED7953FF","#8405A7FF"),labels=c("MNW-B","MNW-F"))+
  theme(legend.background=element_rect(colour="black",fill='white',linetype='solid'),legend.position=c(0.02,0.85),text=element_text(family="Times"))

month <- ggplot(spec,aes(x=time,y=temp,color=site,group=site,linetype=site))+
  geom_smooth(aes(color=site,group=site,fill=site))+
  scale_x_discrete(breaks=c("02:00","12:00","22:00"),labels=c("2am","12pm","10pm"))+
  theme_cowplot()+
  xlab("Time")+
  ylab("Temperature (˚C)")+
  scale_fill_manual(name="Site-RZ",values=c("rosybrown1","thistle1"),labels=c("MNW-B","MNW-F"))+
  scale_color_manual(name="Site-RZ",values=c("#ED7953FF","#8405A7FF"),labels=c("MNW-B","MNW-F"))+
  #theme(legend.background=element_rect(colour="black",fill='white',linetype='solid'),legend.position=c(0.02,0.85),text=element_text(family="Times"))+
  theme(legend.position=c(0.02,0.85))+
  scale_linetype_manual(name="Site-RZ",values=c("solid","twodash"),labels=c("MNW-B","MNW-F"))

ggarrange(month,var,nrow=1,ncol=2,widths=c(1.4,1),labels=c("B.","C."))

#just 1 day in the life
day <- spec %>%
  filter(as.Date(spec$date) == as.Date("2013-07-26"))

#month <- summarySE(spec3,measurevar="temp",groupvars=c("site","time"),na.rm = TRUE)
ggplot(day,aes(x=time,y=temp,color=site,group=site))+
  geom_path(aes(color=site,group=site))+
  theme_cowplot()+
  xlab("Time")+
  ylab("Temperature (˚C)")+
  scale_x_discrete(breaks=c("01:00","12:00","22:00"),labels=c("1am","12pm","10pm"))+
  scale_color_manual(name="Site",values=c("coral","cyan3"),labels=c("MNW-B","MNW-F"))+
  theme(legend.background=element_rect(colour="black",fill='white',linetype='solid'),legend.position=c(0.02,0.85),text=element_text(family="Times"))

ggarrange(month,var,nrow=1,ncol=2)

#### stats round 2 ####
#mean
shapiro.test(range$temp.m)
shapiro.test(log(range$temp.m))
#just not gonna work

wilcox.test(temp.m~site,data=range) #W = 67254, p-value = 0.822

#levene's test
library(car)

spec$site <- as.factor(spec$site)
leveneTest(temp ~ site, data = spec)
# Levene's Test for Homogeneity of Variance (center = median)
#          Df F value Pr(>F)
# group     1   1.604 0.2054
#       17518  

spec$site <- as.factor(spec$site)
leveneTest(temp ~ site, data = spec,center=mean)

#now variance
shapiro.test(log(range$temp.v))
qqPlot(log(range$temp.v))

wilcox.test(log(temp.v)~site,data=range)
wilcox.test(temp.v~site,data=range) #very sig
```

```{r session info}
sessionInfo()
```

```{r script graveyard, include=FALSE, eval=FALSE}
# #line plots - not using
# nuts$month <- as.factor(nuts$month)
# 
# ggplot(nuts,aes(x=month,y=Nitrates_NO3_uM,group=habitat,color=habitat))+
#   geom_path()+
#   facet_wrap(~year)
# 
# # Fancy rain plots - not using {.tabset}
# 
# #install.packages("ggdist")
# library(ggdist)
# #install.packages("gghalves")
# library(gghalves)
# 
# gg.phos <- ggplot(nuts, aes(x = habitat, y = Phosphate_P2O5_uM,color=habitat,shape=habitat,fill=habitat))+ 
#   ggdist::stat_halfeye(
#     adjust = .5, 
#     width = .6, 
#     justification = -.2, 
#     .width = 0, 
#     point_colour = NA,
#     alpha=0.5
#   ) + 
#   geom_boxplot(
#     width = .12, 
#     outlier.color = NA, ## `outlier.shape = NA` works as well
#     alpha=0.5
#   ) +
#   gghalves::geom_half_point(
#     side = "l", 
#     range_scale = .4,
#     alpha=0.5
#   )+
#   theme_cowplot()+
#   xlab("Habitat")+
#   theme(legend.position="none")+
#   scale_shape_manual(values=c(16,15))+
#   scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
#   scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
#   ylab("Phosphates (µM)")
# gg.phos
# 
# gg.nita <- ggplot(nuts, aes(x = habitat, y = Nitrates_NO3_uM,color=habitat,shape=habitat,fill=habitat))+ 
#   ggdist::stat_halfeye(
#     adjust = .5, 
#     width = .6, 
#     justification = -.2, 
#     .width = 0, 
#     point_colour = NA,
#     alpha=0.5
#   ) + 
#   geom_boxplot(
#     width = .12, 
#     outlier.color = NA, ## `outlier.shape = NA` works as well
#     alpha=0.5
#   ) +
#   gghalves::geom_half_point(
#     side = "l", 
#     range_scale = .4,
#     alpha=0.5
#   )+
#   theme_cowplot()+
#   xlab("Habitat")+
#   theme(legend.position="none")+
#   scale_shape_manual(values=c(16,15))+
#   scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
#   scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
#   ylab("Nitrates (µM)")
# gg.nita
# 
# gg.niti <- ggplot(nuts, aes(x = habitat, y = Nitrites_NO2_uM,color=habitat,shape=habitat,fill=habitat))+ 
#   ggdist::stat_halfeye(
#     adjust = .5, 
#     width = .6, 
#     justification = -.2, 
#     .width = 0, 
#     point_colour = NA,
#     alpha=0.5
#   ) + 
#   geom_boxplot(
#     width = .12, 
#     outlier.color = NA, ## `outlier.shape = NA` works as well
#     alpha=0.5
#   ) +
#   gghalves::geom_half_point(
#     side = "l", 
#     range_scale = .4,
#     alpha=0.5
#   )+
#   theme_cowplot()+
#   xlab("Habitat")+
#   theme(legend.position="none")+
#   scale_shape_manual(values=c(16,15))+
#   scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
#   scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
#   ylab("Nitrites (µM)")
# gg.niti
# 
# gg.sili <- ggplot(nuts, aes(x = habitat, y = Silice_SiO2_uM,color=habitat,shape=habitat,fill=habitat))+ 
#   ggdist::stat_halfeye(
#     adjust = .5, 
#     width = .6, 
#     justification = -.2, 
#     .width = 0, 
#     point_colour = NA,
#     alpha=0.5
#   ) + 
#   geom_boxplot(
#     width = .12, 
#     outlier.color = NA, ## `outlier.shape = NA` works as well
#     alpha=0.5
#   ) +
#   gghalves::geom_half_point(
#     side = "l", 
#     range_scale = .4,
#     alpha=0.5
#   )+
#   theme_cowplot()+
#   xlab("Habitat")+
#   theme(legend.position="none")+
#   scale_shape_manual(values=c(16,15))+
#   scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
#   scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
#   ylab("Silica (µM)")
# gg.sili
# 
# gg.ammo <- ggplot(nuts, aes(x = habitat, y = Ammonium_NH4_uM,color=habitat,shape=habitat,fill=habitat))+ 
#   ggdist::stat_halfeye(
#     adjust = .5, 
#     width = .6, 
#     justification = -.2, 
#     .width = 0, 
#     point_colour = NA,
#     alpha=0.5
#   ) + 
#   geom_boxplot(
#     width = .12, 
#     outlier.color = NA, ## `outlier.shape = NA` works as well
#     alpha=0.5
#   ) +
#   gghalves::geom_half_point(
#     side = "l", 
#     range_scale = .4,
#     alpha=0.5
#   )+
#   theme_cowplot()+
#   xlab("Habitat")+
#   theme(legend.position="none")+
#   scale_shape_manual(values=c(16,15))+
#   scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
#   scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
#   ylab("Ammonium (µM)")
# gg.ammo

#variance - nothing interesting here

#library(car)
        
# nuts$habitat <- as.factor(nuts$habitat)
# leveneTest(Phosphate_P2O5_uM~habitat,data=nuts)
# leveneTest(Nitrates_NO3_uM~habitat,data=nuts)
# leveneTest(Nitrites_NO2_uM~habitat,data=nuts)
# leveneTest(Silice_SiO2_uM~habitat,data=nuts)
# leveneTest(Ammonium_NH4_uM~habitat,data=nuts)

#range - nothing interesting

# nuts.back <- subset(nuts,habitat=="Back reef")
# nuts.fore <- subset(nuts,habitat=="Fore reef")
# 
# var(nuts.back$Phosphate_P2O5_uM)
# var(nuts.fore$Phosphate_P2O5_uM)
# 
# (max(nuts.back$Phosphate_P2O5_uM)-min(nuts.back$Phosphate_P2O5_uM))
# (max(nuts.fore$Phosphate_P2O5_uM)-min(nuts.fore$Phosphate_P2O5_uM))
# 
# var(nuts.back$Nitrates_NO3_uM)
# var(nuts.fore$Nitrates_NO3_uM)
# 
# (max(nuts.back$Nitrates_NO3_uM)-min(nuts.back$Nitrates_NO3_uM))
# (max(nuts.fore$Nitrates_NO3_uM)-min(nuts.fore$Nitrates_NO3_uM))
# 
# var(nuts.back$Nitrites_NO2_uM)
# var(nuts.fore$Nitrites_NO2_uM)
# 
# (max(nuts.back$Nitrites_NO2_uM)-min(nuts.back$Nitrites_NO2_uM))
# (max(nuts.fore$Nitrites_NO2_uM)-min(nuts.fore$Nitrites_NO2_uM))
# 
# var(nuts.back$Nitrites_NO2_uM)
# var(nuts.fore$Nitrites_NO2_uM)
# 
# (max(nuts.back$Nitrites_NO2_uM)-min(nuts.back$Nitrites_NO2_uM))
# (max(nuts.fore$Nitrites_NO2_uM)-min(nuts.fore$Nitrites_NO2_uM))
```
<<<<<<< HEAD
=======

>>>>>>> be92149c87bdd293bfde9e9b9b6c2f6815f28342
