---
title: "Environmental data"
author: "Nicola G. Kriefall"
date: "6/30/2021"
output:
 rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: haddock
    number_sections: true
    #code_folding: hide
---

```{r setup, include=FALSE}
#work computer 
#setwd("~/nicfall drive/Moorea_revisions/env_revised")
#home computer
#setwd("/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/")
```

## Setup - load packages

```{r packages}
library(ggplot2)
library(cowplot)
library(dplyr)
library(colorBlindness)
library(scales)
library(bestNormalize)
library(Rmisc)
library(ggpubr)
```

# Substrate composition

```{r data processing}
sub.tah <- read.csv('/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/substrate.csv',header=TRUE)

sub <- subset(sub.tah,Marine.Area!="Tahiti Faaa")

sub$Substrate <- as.factor(sub$Substrate)
#str(sub)
##total proportion
sub$prop.test <- (sub$proportion)/3

##rename sites & habitats
sub$Marine.Area <- as.factor(sub$Marine.Area)
levels(sub$Marine.Area)
levels(sub$Marine.Area) <- c("Mo'orea SE","Mo'orea NW")
levels(sub$Marine.Area)
sub$Marine.Area <- factor(sub$Marine.Area, levels=c("Mo'orea NW","Mo'orea SE")) #reorder

sub$Habitat <- as.factor(sub$Habitat)
levels(sub$Habitat)
levels(sub$Habitat) <- c("Back","Fore")
levels(sub$Habitat)

##only interested in 2013 - year of collection
sub13 <- subset(sub,Year=="2013")
sub14 <- subset(sub,Year=="2014")
```

## Plots {.tabset}

### Figure - all the categories

```{r plot2}
ggplot(data=sub13, aes(x=Habitat, y=prop.test, fill=Substrate)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')

ggplot(data=sub14, aes(x=Habitat, y=prop.test, fill=Substrate)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')

#ggsave("substrate.png")
```

### Figure - summed categories

```{r plot summed cats}
sub13$Substrate <- gsub(" ","_",sub13$Substrate)

sub13$sub_cats <- recode(sub13$Substrate, Acropora="Coral", Asparagopsis="Algae", Cyanophyceae="Algae", Dead_coral="Abiotic substrata", Dictyota="Algae", Halimeda="Algae", Macroalgae="Algae", Millepora="Coral", Montastrea="Coral", Montipora="Coral", Napopora="Coral", Pavement="Abiotic substrata", Pavona="Coral", Pocillopora="Coral", Porites="Coral", Psammocora="Coral", Rubble="Abiotic substrata", Sand="Abiotic substrata", Stegastes_Turf="Algae", Synarea="Coral", Turbinaria="Coral")

pal <- hcl.colors(12,"Tofino")
show_col(pal)
colorz <- c("#3B415E","#8FC67C","#818CC0")

sub3 <- ggplot(data=sub13, aes(x=Habitat, y=prop.test, fill=sub_cats)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
  scale_fill_manual(values=colorz,name="Substrate",labels=c("Abiotic","Algae","Coral"))

sub3

#cvdPlot(sub3)

#ggsave("substrate_3cats.png",height=3.5) #can also go back to default if square

sub14$Substrate <- gsub(" ","_",sub14$Substrate)

sub14$sub_cats <- recode(sub14$Substrate, Acropora="Coral", Asparagopsis="Algae", Cyanophyceae="Algae", Dead_coral="Abiotic substrata", Dictyota="Algae", Halimeda="Algae", Macroalgae="Algae", Millepora="Coral", Montastrea="Coral", Montipora="Coral", Napopora="Coral", Pavement="Abiotic substrata", Pavona="Coral", Pocillopora="Coral", Porites="Coral", Psammocora="Coral", Rubble="Abiotic substrata", Sand="Abiotic substrata", Stegastes_Turf="Algae", Synarea="Coral", Turbinaria="Coral")

pal <- hcl.colors(12,"Tofino")
show_col(pal)
colorz <- c("#3B415E","#8FC67C","#818CC0")

sub4 <- ggplot(data=sub14, aes(x=Habitat, y=prop.test, fill=sub_cats)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
  scale_fill_manual(values=colorz,name="Substrate",labels=c("Abiotic","Algae","Coral"))

sub4
```

### Figure - medium categories

```{r medium categories}
sub13$sub_cats_med <- recode(sub13$Substrate, Acropora="Coral - Acropora", Asparagopsis="Algae - Asparagopsis", Cyanophyceae="Algae - Cyanophyceae", Dead_coral="Abiotic (e.g. rubble, sand)", Dictyota="Algae - Dictyota", Halimeda="Algae - Halimeda", Macroalgae="Algae - Macroalgae", Millepora="Coral - Millepora", Montastrea="Coral - Montastrea", Montipora="Coral - Montipora", Napopora="Coral - Napopora", Pavement="Abiotic (e.g. rubble, sand)", Pavona="Coral - Pavona", Pocillopora="Coral - Pocillopora", Porites="Coral - Porites", Psammocora="Coral - Psammocora", Rubble="Abiotic (e.g. rubble, sand)", Sand="Abiotic (e.g. rubble, sand)", Stegastes_Turf="Algae - Stegastes Turf", Synarea="Coral - Synarea", Turbinaria="Coral - Turbinaria")  

#greens for algae
#pal.gr <- hcl.colors(5,"Greens")
#show_col(pal.gr)
#pal.gr
#"#004616" "#30893B" "#81C07A" "#CAE8C1" "#F6FBF4"
#pal.bl <- hcl.colors(9,"BuPu")
#show_col(pal.bl)
#pal.bl
#"#540046" "#6E2072" "#8346A1" "#8674B8" "#9099CA" "#A3BAD9" "#BED6E6" "#DBECF3" "#F2FBFC"

colorz2 <- c("grey","#004616","#30893B","#81C07A","#CAE8C1","#F6FBF4","#540046","#6E2072","#8346A1","#8674B8","#9099CA","#A3BAD9","#BED6E6","#DBECF3","#F2FBFC")

sub.med <- ggplot(data=sub13, aes(x=Habitat, y=prop.test, fill=sub_cats_med)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
 scale_fill_manual(values=colorz2,name="Substrate")

sub.med
#ggsave("substrate_medcats.png",height=4) #can also go back to default if square
#cvdPlot(sub.med)

sub14$sub_cats_med <- recode(sub14$Substrate, Acropora="Coral - Acropora", Asparagopsis="Algae - Asparagopsis", Cyanophyceae="Algae - Cyanophyceae", Dead_coral="Abiotic (e.g. rubble, sand)", Dictyota="Algae - Dictyota", Halimeda="Algae - Halimeda", Macroalgae="Algae - Macroalgae", Millepora="Coral - Millepora", Montastrea="Coral - Montastrea", Montipora="Coral - Montipora", Napopora="Coral - Napopora", Pavement="Abiotic (e.g. rubble, sand)", Pavona="Coral - Pavona", Pocillopora="Coral - Pocillopora", Porites="Coral - Porites", Psammocora="Coral - Psammocora", Rubble="Abiotic (e.g. rubble, sand)", Sand="Abiotic (e.g. rubble, sand)", Stegastes_Turf="Algae - Stegastes Turf", Synarea="Coral - Synarea", Turbinaria="Coral - Turbinaria")  

#greens for algae
pal.gr <- hcl.colors(5,"Greens")
show_col(pal.gr)
pal.gr
#"#004616" "#30893B" "#81C07A" "#CAE8C1" "#F6FBF4"
pal.bl <- hcl.colors(9,"BuPu")
show_col(pal.bl)
pal.bl
#"#540046" "#6E2072" "#8346A1" "#8674B8" "#9099CA" "#A3BAD9" "#BED6E6" "#DBECF3" "#F2FBFC"

colorz2 <- c("grey","#004616","#30893B","#81C07A","#CAE8C1","#F6FBF4","#540046","#6E2072","#8346A1","#8674B8","#9099CA","#A3BAD9","#BED6E6","#DBECF3","#F2FBFC")

sub.med2 <- ggplot(data=sub14, aes(x=Habitat, y=prop.test, fill=sub_cats_med)) +
  geom_bar(stat="identity")+
  facet_wrap(~Marine.Area)+ #just need to remove 'nrow' here to go back to grid
  theme_cowplot()+
  ylab('Relative proportion')+
  xlab('Reef zone')+
 scale_fill_manual(values=colorz2,name="Substrate")

sub.med2
#ggsave("substrate_medcats.png",height=4) #can also go back to default if square
#cvdPlot(sub.med)
```

## Synthesizing

```{r}
ggarrange(sub.med,sub.med2,common.legend=TRUE,legend="right")
```

```{r, eval=FALSE, include=FALSE}
#Tahiti didn't really work

# tah <- subset(sub.tah,Marine.Area=="Tahiti Faaa")
# 
# tah$Substrate <- gsub(" ","_",tah$Substrate)
# 
# tah$sub_cats <- recode(tah$Substrate, Acropora="Coral", Montipora="Coral", Pavona="Coral", Pocillopora="Coral", Porites="Coral", Astrea_curta="Coral", Leptastrea="Coral", Autres="Coral")  
# 
# tah$sub_cats_med <- recode(tah$Substrate, Acropora="Coral - Acropora", Montipora="Coral - Montipora", Pavona="Coral - Pavona", Pocillopora="Coral - Pocillopora", Porites="Coral - Porites", Astrea_curta="Coral - Astrea curta", Leptastrea="Coral - Leptastrea", Autres="Coral - Autres")  
# 
# sub.coral <- subset(sub13,sub_cats=="Coral")
# 
# tah$prop.test <- (tah$proportion)/20
# 
# corals <- rbind(tah,sub.coral)
# 
# ggplot(data=corals, aes(x=Habitat, y=prop.test, fill=Substrate)) +
#   geom_bar(stat="identity")+
#   facet_wrap(~Marine.Area)+
#   theme_cowplot()+
#   ylab('Relative proportion')+
#   xlab('Reef zone')                    
```

# Nutrients

```{r read in nutrient data}
nuts <- read.csv("/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/nuts_13-14_renamed.csv",header=T)
str(nuts)
```

## From revisions - by month {.tabset}

### Phosphate revised

```{r}
nuts$ym <- paste0(nuts$year,"_",nuts$month)
nuts$date2 <- as.Date(nuts$date,"%m/%d/%y")
str(nuts)

gg.new.pho <- ggplot(nuts,aes(x=date2,y=Phosphate_P2O5_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Phosphates (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.pho
```

### Nitrates revised

```{r}
gg.new.nia <- ggplot(nuts,aes(x=date2,y=Nitrates_NO3_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Nitrates (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.nia
```

### Nitrites revised

```{r}
gg.new.nii <- ggplot(nuts,aes(x=date2,y=Nitrites_NO2_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Nitrites (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.nii
```

### Silica revised

```{r}
gg.new.sil <- ggplot(nuts,aes(x=date2,y=Silice_SiO2_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Silica (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.sil
```

### Ammonium revised

```{r}
gg.new.amm <- ggplot(nuts,aes(x=date2,y=Ammonium_NH4_uM,color=habitat,group=habitat,shape=habitat))+
  geom_line()+
  theme_cowplot()+
  geom_point()+
  geom_vline(xintercept=as.numeric(as.Date("2013-07-26")),linetype=4)+
  geom_vline(xintercept=as.numeric(as.Date("2013-08-09")),linetype=4)+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  #theme(legend.position="none")+
  xlab("")+
  ylab("Ammonium (µM)")+
  labs(color="Habitat",shape="Habitat")
gg.new.amm
```

## Results summarized - revised

```{r multipanel revised}
ggarrange(gg.new.pho,gg.new.nia,gg.new.nii,gg.new.sil,gg.new.amm,labels="AUTO",common.legend=TRUE,legend="right",nrow=5)
#ggsave("env_nutrients_revised.pdf",height=12)
```

## Box plots

### Wrap by year

```{r box plots x year}
ggplot(nuts,aes(x=habitat,y=Phosphate_P2O5_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Nitrates_NO3_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Nitrites_NO2_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Silice_SiO2_uM))+
  geom_boxplot()+
  facet_wrap(~year)

ggplot(nuts,aes(x=habitat,y=Ammonium_NH4_uM))+
  geom_boxplot()+
  facet_wrap(~year)
```

## Violin plots {.tabset}

### Phosphates

```{r violin phos}
gg.pho <- ggplot(nuts,aes(x=habitat,y=Phosphate_P2O5_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.7)+
  theme_cowplot()+
  geom_boxplot(width=0.1,alpha=0)+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Phosphates (µM)")
gg.pho

library(car)

nuts$habitat <- as.factor(nuts$habitat)
shapiro.test(log(nuts$Phosphate_P2O5_uM))
leveneTest(nuts$Phosphate_P2O5_uM,nuts$habitat)#ns

summary(aov(Phosphate_P2O5_uM~habitat,data=nuts)) #ns
#wilcox.test(Phosphate_P2O5_uM~habitat,data=nuts,exact=FALSE) #ns
```

### Nitrates

```{r violin nitra}
gg.nia <- ggplot(nuts,aes(x=habitat,y=Nitrates_NO3_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.7)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Nitrates (µM)")
gg.nia

shapiro.test(log(nuts$Nitrates_NO3_uM)) #no
leveneTest(nuts$Nitrates_NO3_uM,nuts$habitat)#ns

#summary(aov(Nitrates_NO3_uM~habitat,data=nuts)) #p < 0.01**
wilcox.test(Nitrates_NO3_uM~habitat,data=nuts,exact=FALSE) #p < 0.01**
# Wilcoxon rank sum test with continuity correction
# 
# data:  Nitrates_NO3_uM by habitat
# W = 435, p-value = 0.002519

sum.nia <- summarySE(data=nuts,measurevar="Nitrates_NO3_uM",groupvars="habitat")
sum.nia
```

### Nitrites

```{r violin nitrites}
gg.nii <- ggplot(nuts,aes(x=habitat,y=Nitrites_NO2_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.7)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Nitrites (µM)")
gg.nii

shapiro.test(nuts$Nitrites_NO2_uM)

#summary(aov(Nitrites_NO2_uM~habitat,data=nuts)) #p < 0.05*
wilcox.test(Nitrites_NO2_uM~habitat,data=nuts,exact=FALSE) #p < 0.01**

sum.nii <- summarySE(data=nuts,measurevar="Nitrites_NO2_uM",groupvars="habitat")
sum.nii
```

### Silica

```{r violin sili}
gg.sil <- ggplot(nuts,aes(x=habitat,y=Silice_SiO2_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.5)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Silica (µM)")
gg.sil
summary(aov(Silice_SiO2_uM~habitat,data=nuts)) #ns
wilcox.test(Silice_SiO2_uM~habitat,data=nuts) #ns
```

### Ammonium

```{r violin ammo}
gg.amm <- ggplot(nuts,aes(x=habitat,y=Ammonium_NH4_uM,color=habitat,shape=habitat))+
  geom_violin()+
  #geom_jitter(alpha=0.5)+
  geom_boxplot(width=0.1,alpha=0)+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15),labels=c("BR","FR"))+
  scale_x_discrete(labels=c("BR","FR"))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"),labels=c("Back reef","Fore reef"))+
  theme(legend.position="none")+
  xlab("Habitat")+
  ylab("Ammonium (µM)")
gg.amm
summary(aov(Ammonium_NH4_uM~habitat,data=nuts)) #ns
wilcox.test(Ammonium_NH4_uM~habitat,data=nuts) #ns
```

## Multipanel violin plot

Results: 
- phosphates not sig, log-transformed anova
- nitrates
- nitrites
- silica
- ammonium

```{r}
library(ggpubr)

ggarrange(gg.pho,gg.nia,gg.nii,gg.sil,gg.amm,labels="AUTO")
#ggsave("env_nutrients.pdf",width=7)

```

# Flow

```{r flow data}
flowdat <- read.csv("/Volumes/Macintosh HD/Users/nicolakriefall/Google Drive (nicfall@bu.edu)/Moorea_revisions/env_revised/flow_rates_reformatted.csv",header=T)



ggplot(flowdat,aes(x=site,y=speed_ms,fill=site))+
  geom_boxplot()+
  theme_cowplot()+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Flow (m/s)")+
  xlab("Site-reef zone")+
  theme(legend.position="none")
#ggsave("mnw.flow.pdf",width=2.5,height=2)

best.speed <- bestNormalize(flowdat$speed_ms)
flowdat$speed.t <- best.speed$x.t

a.flow <- aov(speed.t~site,data=flowdat)
summary(a.flow)
plot(a.flow)


flow.sd <- summarySE(data=flowdat,measurevar="speed_ms",groupvars="site")
flow.sd
```
















```{r script graveyard, include=FALSE, eval=FALSE}
#line plots - not using
nuts$month <- as.factor(nuts$month)

ggplot(nuts,aes(x=month,y=Nitrates_NO3_uM,group=habitat,color=habitat))+
  geom_path()+
  facet_wrap(~year)

# Fancy rain plots - not using {.tabset}

#install.packages("ggdist")
library(ggdist)
#install.packages("gghalves")
library(gghalves)

gg.phos <- ggplot(nuts, aes(x = habitat, y = Phosphate_P2O5_uM,color=habitat,shape=habitat,fill=habitat))+ 
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    justification = -.2, 
    .width = 0, 
    point_colour = NA,
    alpha=0.5
  ) + 
  geom_boxplot(
    width = .12, 
    outlier.color = NA, ## `outlier.shape = NA` works as well
    alpha=0.5
  ) +
  gghalves::geom_half_point(
    side = "l", 
    range_scale = .4,
    alpha=0.5
  )+
  theme_cowplot()+
  xlab("Habitat")+
  theme(legend.position="none")+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Phosphates (µM)")
gg.phos

gg.nita <- ggplot(nuts, aes(x = habitat, y = Nitrates_NO3_uM,color=habitat,shape=habitat,fill=habitat))+ 
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    justification = -.2, 
    .width = 0, 
    point_colour = NA,
    alpha=0.5
  ) + 
  geom_boxplot(
    width = .12, 
    outlier.color = NA, ## `outlier.shape = NA` works as well
    alpha=0.5
  ) +
  gghalves::geom_half_point(
    side = "l", 
    range_scale = .4,
    alpha=0.5
  )+
  theme_cowplot()+
  xlab("Habitat")+
  theme(legend.position="none")+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Nitrates (µM)")
gg.nita

gg.niti <- ggplot(nuts, aes(x = habitat, y = Nitrites_NO2_uM,color=habitat,shape=habitat,fill=habitat))+ 
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    justification = -.2, 
    .width = 0, 
    point_colour = NA,
    alpha=0.5
  ) + 
  geom_boxplot(
    width = .12, 
    outlier.color = NA, ## `outlier.shape = NA` works as well
    alpha=0.5
  ) +
  gghalves::geom_half_point(
    side = "l", 
    range_scale = .4,
    alpha=0.5
  )+
  theme_cowplot()+
  xlab("Habitat")+
  theme(legend.position="none")+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Nitrites (µM)")
gg.niti

gg.sili <- ggplot(nuts, aes(x = habitat, y = Silice_SiO2_uM,color=habitat,shape=habitat,fill=habitat))+ 
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    justification = -.2, 
    .width = 0, 
    point_colour = NA,
    alpha=0.5
  ) + 
  geom_boxplot(
    width = .12, 
    outlier.color = NA, ## `outlier.shape = NA` works as well
    alpha=0.5
  ) +
  gghalves::geom_half_point(
    side = "l", 
    range_scale = .4,
    alpha=0.5
  )+
  theme_cowplot()+
  xlab("Habitat")+
  theme(legend.position="none")+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Silica (µM)")
gg.sili

gg.ammo <- ggplot(nuts, aes(x = habitat, y = Ammonium_NH4_uM,color=habitat,shape=habitat,fill=habitat))+ 
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    justification = -.2, 
    .width = 0, 
    point_colour = NA,
    alpha=0.5
  ) + 
  geom_boxplot(
    width = .12, 
    outlier.color = NA, ## `outlier.shape = NA` works as well
    alpha=0.5
  ) +
  gghalves::geom_half_point(
    side = "l", 
    range_scale = .4,
    alpha=0.5
  )+
  theme_cowplot()+
  xlab("Habitat")+
  theme(legend.position="none")+
  scale_shape_manual(values=c(16,15))+
  scale_colour_manual(values=c("#ED7953FF","#8405A7FF"))+
  scale_fill_manual(values=c("#ED7953FF","#8405A7FF"))+
  ylab("Ammonium (µM)")
gg.ammo

#variance - nothing interesting here

#library(car)
        
# nuts$habitat <- as.factor(nuts$habitat)
# leveneTest(Phosphate_P2O5_uM~habitat,data=nuts)
# leveneTest(Nitrates_NO3_uM~habitat,data=nuts)
# leveneTest(Nitrites_NO2_uM~habitat,data=nuts)
# leveneTest(Silice_SiO2_uM~habitat,data=nuts)
# leveneTest(Ammonium_NH4_uM~habitat,data=nuts)

#range - nothing interesting

# nuts.back <- subset(nuts,habitat=="Back reef")
# nuts.fore <- subset(nuts,habitat=="Fore reef")
# 
# var(nuts.back$Phosphate_P2O5_uM)
# var(nuts.fore$Phosphate_P2O5_uM)
# 
# (max(nuts.back$Phosphate_P2O5_uM)-min(nuts.back$Phosphate_P2O5_uM))
# (max(nuts.fore$Phosphate_P2O5_uM)-min(nuts.fore$Phosphate_P2O5_uM))
# 
# var(nuts.back$Nitrates_NO3_uM)
# var(nuts.fore$Nitrates_NO3_uM)
# 
# (max(nuts.back$Nitrates_NO3_uM)-min(nuts.back$Nitrates_NO3_uM))
# (max(nuts.fore$Nitrates_NO3_uM)-min(nuts.fore$Nitrates_NO3_uM))
# 
# var(nuts.back$Nitrites_NO2_uM)
# var(nuts.fore$Nitrites_NO2_uM)
# 
# (max(nuts.back$Nitrites_NO2_uM)-min(nuts.back$Nitrites_NO2_uM))
# (max(nuts.fore$Nitrites_NO2_uM)-min(nuts.fore$Nitrites_NO2_uM))
# 
# var(nuts.back$Nitrites_NO2_uM)
# var(nuts.fore$Nitrites_NO2_uM)
# 
# (max(nuts.back$Nitrites_NO2_uM)-min(nuts.back$Nitrites_NO2_uM))
# (max(nuts.fore$Nitrites_NO2_uM)-min(nuts.fore$Nitrites_NO2_uM))
```

```{r session info}
sessionInfo()
```
